---
title: "Report from MinkSim"
author: "K?ri Gautason"
date: "2 sep 2016"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

# Results from MinkSim

A variety of key figures and plots will be generated

## Table of Contents
  1. Litter size and reproduction results
  2. Body weight and skin length
  3. Live graded quality and skin quality
  4. Feeding costs
  5. Economics

##   1. Litter size and reproduction results

### Summary statistics
```{r results="asis", echo=FALSE}
library(ggplot2)
  # setwd("C:/Users/au384062/Dropbox/Projects/Kopenhagen Fur/Analysis results/Scenarios/Skejby_0811/Standard/Raw_Data//")
   # setwd("C:/Users/au384062/Dropbox/Projects/simulation of mink farm/Output/DMU analysis")
   setwd("C:/Users/au384062/Dropbox/Projects/Kopenhagen Fur/Analysis results/Scenarios/Economic_values_1/Litter_size2/raw_data")


library(doBy)        #
    results <- read.table("results", header = T, row.names = NULL)

summarized <-
  summaryBy(
      Gen + Gmean + Gvar + Fis + Obs.fert + mean.phenotype.bw.females + gen.value.bs +
        mean.phenotype.bw.males + bw.var+cor.bw.phenotype +
        skin.length.mean+
        skin.length.var+
        skin.qual.mean+
        skin.qual.var+
        cor.ls.own.to.ls+mated.females+barren.females+numb.false.sires+numb.kits+
        remating.perc+perc.single.mat+mean.gen.val.qual+var.gen.val.qual+survived.kits+
        avg.skin.length.male+avg.skin.length.female+feed.per.skin+skin.price+
      margin+feeding.cost.pr.skin+avg.skin.price+margin+income.from.skins+variable.costs+fixed.costs+pelting.costs+income.fr.sold.kits+
        gross.feeding.costs+cage_utilization+n.females+sold.skins+costs.pr.sold.skin+costs.pr.female

    ~ Gen,
    data = results,
    FUN = c(mean, var),
    na.rm = T
  )



data <- matrix(c(
              "Mated females",
               "Barren females%",
               "% kits w false sires",
               "% females with same male 2", 
               "% females single-mated",
               round( mean(summarized$mated.females.mean),2), 
               round(mean(summarized$barren.females.mean)/mean(summarized$mated.females.mean)*100,2),
               round((1-mean(summarized$numb.false.sires.mean))*100,2), 
               round(mean(summarized$remating.perc.mean*100),2),
               round(mean(summarized$perc.single.mat.mean)*100),2),
               nrow = 5, ncol = 2)
knitr::kable(data, caption= "Key Figures",digits = 2)
```

### Cage use
This shows how big a proportion of the cages were occupied in each year of the simulation 

```{r ,echo=FALSE}


qplot(Gen, cage_utilization.mean, data = summarized) + geom_errorbar(
  aes(
    x = Gen,
    ymin = cage_utilization.mean - sqrt(cage_utilization.var),
    ymax = cage_utilization.mean + sqrt(cage_utilization.var)
  ),
  width = 0.25,
  data = summarized
) + geom_line(linetype =2)+labs( title = "Cage usage", x= "Year of simulation", y= "Proportion")

```

### Litter size per mated female
This is defined as kits born alive. Bars show standard deviation of each replicate.

```{r summarized,echo=FALSE}


qplot(Gen, Obs.fert.mean, data = summarized) + geom_errorbar(
  aes(
    x = Gen,
    ymin = Obs.fert.mean - sqrt(Obs.fert.var),
    ymax = Obs.fert.mean + sqrt(Obs.fert.var)
  ),
  width = 0.25,
  data = summarized
) + geom_line(linetype =2)+labs( title = "Kits per mated female", x= "Year of simulation", y= "kits/female")

```

### Genetic trend for litter size

Genetic trend of litter size within age cohort

```{r, echo=FALSE}
qplot(Gen, Gmean.mean, data = summarized) + geom_errorbar(
  aes(
    x = Gen,
    ymin = Gmean.mean - sqrt(Gmean.var),
    ymax = Gmean.mean + sqrt(Gmean.var)
  ),
  width = 0.25,
  data = summarized
) + geom_line(linetype =2)+
  labs( title = "Genetic trend of litter size", x= "Year of simulation", y= "mean genetic value of LS")
```

### Genetic variance of litter size

Shows the trend in the genetic variance of litter size through the simulation. Theoretically it should slowly decrease over time. Increase indicates assortative mating or possible, a bug.

```{r, echo=FALSE}
qplot(Gen, Gvar.mean, data = summarized) + geom_errorbar(
  aes(
    x = Gen,
    ymin = Gvar.mean - sqrt(Gvar.var),
    ymax = Gvar.mean + sqrt(Gvar.var)
  ),
  width = 0.25,
  data = summarized
) + geom_line(linetype =2)+labs( title = "Genetic variance of litter size", x= "Year of simulation", y= "Genetic variance")

```

### Inbreeding coefficient

Program tracks inbreeding through the simulation. 

```{r, echo=FALSE}
qplot(Gen, Fis.mean, data = summarized) + geom_errorbar(
  aes(
    x = Gen,
    ymin = Fis.mean - sqrt(Fis.var),
    ymax = Fis.mean + sqrt(Fis.var)
  ),
  width = 0.25,
  data = summarized
) + geom_line(linetype =2)+labs( title = "Inbreeding Coefficient", x= "Year of simulation", y= "F")

```

### Accuracy of selection criterion

This is defined as the correlation between the phenotype of the kits dam to the true breeding value of the kit

```{r, echo=FALSE}
qplot(Gen, cor.ls.own.to.ls.mean, data = summarized) + geom_errorbar(
  aes(
    x = Gen,
    ymin = cor.ls.own.to.ls.mean - sqrt(cor.ls.own.to.ls.var),
    ymax = cor.ls.own.to.ls.mean + sqrt(cor.ls.own.to.ls.var)
  ),
  width = 0.25,
  data = summarized
) + geom_line(linetype =2)+
  labs( title = "Accuracy of phenotype as selection criterion", x= "Year of simulation", y= "Cor( Ydam,TBV )")

```


## 2. Body weight and skin length

### Body weight of females
Body weight of females at 205 days of age, mean within age cohort. 

```{r, echo=FALSE}

qplot(Gen, mean.phenotype.bw.females.mean, data = summarized) + geom_errorbar(
  aes(
    x = Gen,
    ymin = mean.phenotype.bw.females.mean - sqrt(mean.phenotype.bw.females.var),
    ymax = mean.phenotype.bw.females.mean + sqrt(mean.phenotype.bw.females.var)
  ),
  width = 0.25,
  data = summarized
) + geom_line(linetype =2) +
  labs(title = "Mean body weight of females", x="Simulation Year", y="Body Weight [kg]")
```
### Body weight of males
Body weight of males at 205 days of age, mean within age cohort. 
```{r,echo=FALSE}
qplot(Gen, mean.phenotype.bw.males.mean, data = summarized) + geom_errorbar(
  aes(
    x = Gen,
    ymin = mean.phenotype.bw.males.mean - sqrt(mean.phenotype.bw.males.var),
    ymax = mean.phenotype.bw.males.mean + sqrt(mean.phenotype.bw.males.var)
  ),
  width = 0.25,
  data = summarized
) + geom_line(linetype =2)+labs(title= "Mean body weight of males", x = "Simulation Year", y = "Body weight [kg]")

```

### Genetic variance of body weight

```{r,echo=FALSE}
qplot(Gen, bw.var.mean, data = summarized) + geom_errorbar(
  aes(
    x = Gen,
    ymin = bw.var.mean - sqrt(bw.var.var),
    ymax = bw.var.mean + sqrt(bw.var.var)
  ),
  width = 0.25,
  data = summarized
) + geom_line(linetype =2)+
  labs(title= "Genetic variance of body weight", x = "Simulation Year", y = "Genetic variance [kg^2]")

```


### Genetic trend of male skin length

```{r,echo=FALSE}
qplot(Gen, skin.length.mean.mean, data = summarized) + geom_errorbar(
  aes(
    x = Gen,
    ymin = skin.length.mean.mean - sqrt(skin.length.var.mean),
    ymax = skin.length.mean.mean + sqrt(skin.length.var.mean)
  ),
  width = 0.25,
  data = summarized
) + geom_line(linetype =2)+
  labs(title= "Genetic trend of skin length", x = "Simulation Year", y = "Genetic variance [kg^2]")

```


### Skin length phenotype, male skins

This shows the development in average skin length, note that this is within age cohort and includes all animals, even those not pelted

```{r,echo=FALSE}
qplot(Gen, avg.skin.length.male.mean, data = summarized) + geom_errorbar(
  aes(
    x = Gen,
    ymin = avg.skin.length.male.mean - sqrt(avg.skin.length.male.var),
    ymax = avg.skin.length.male.mean + sqrt(avg.skin.length.male.var)
  ),
  width = 0.25,
  data = summarized
) + geom_line(linetype =2)+
    labs(title= "Skin length of males", x = "Simulation Year", y = "Skin length [cm]")+
 geom_hline(aes(yintercept=101))+
  annotate("text", x = 11, y = 102, label = "50 size")+
 geom_hline(aes(yintercept=95))+
    annotate("text", x = 11, y = 96, label = "40 size")+
 geom_hline(aes(yintercept=89))+
  annotate("text", x = 11, y = 90, label = "30 size")

```

### Skin length phenotype, female skins

This shows the development in average skin length, note that this is within age cohort and includes all animals, even those not pelted

```{r,echo=FALSE}
qplot(Gen, avg.skin.length.female.mean, data = summarized) + geom_errorbar(
  aes(
    x = Gen,
    ymin = avg.skin.length.female.mean - sqrt(avg.skin.length.female.var),
    ymax = avg.skin.length.female.mean + sqrt(avg.skin.length.female.var)
  ),
  width = 0.25,
  data = summarized
) + geom_line(linetype =2) +
    labs(title= "Skin length of females", x = "Simulation Year", y = "Skin length [cm]")+
 geom_hline(aes(yintercept=83))+
  annotate("text", x = 11, y = 84, label = "0 size")+
 geom_hline(aes(yintercept=77))+
    annotate("text", x = 11, y = 78, label = "1 size")+
 geom_hline(aes(yintercept=71))+
  annotate("text", x = 11, y = 72, label = "2 size")

```

## 3. Skin quality and live graded quality

### Average quality of skins

Note that the unit here is difficult to interpret. It is in phenotypic units, i.e. includes both environment and genetic part. Defined to start as the average distribution of skins in 2015 from Norway, Sweden, Denmark and Iceland. Quality of all other skins sold are fixed.

```{r, echo= FALSE}
qplot(Gen, skin.qual.mean.mean, data = summarized) + geom_errorbar(
  aes(
    x = Gen,
    ymin = skin.qual.mean.mean - sqrt(skin.qual.mean.var),
    ymax = skin.qual.mean.mean + sqrt(skin.qual.mean.var)
  ),
  width = 0.25,
  data = summarized
) + geom_line(linetype =2)+
      labs(title= "Skin quality phenotype", x = "Simulation Year", y = "Skin qual [undefined]")

```



## 4. Feed costs
### Feed costs per produced skin

Note that this is a beta version with all the feeding costs, minus the amount kits eat in weeks 6-9

```{r, echo= FALSE}
qplot(Gen, feeding.cost.pr.skin.mean, data = summarized) + geom_errorbar(
  aes(
    x = Gen,
    ymin = feeding.cost.pr.skin.mean - sqrt(feeding.cost.pr.skin.var),
    ymax = feeding.cost.pr.skin.mean + sqrt(feeding.cost.pr.skin.var)
  ),
  width = 0.25,
  data = summarized
) + geom_line(linetype =2)+
      labs(title= "Feeding cost per produced skin", x = "Simulation Year", y = "Feeding costs [DKK]")

```

## 5. Economics

Here i will put in economical analyses of the runs, given some assumptions. I want to include margin pr farm, pr female and pr skin

### Average skin price across farm

Here is the raw average of sold skins. It is important to keep in mind that there is a bias upwards in this price when the litter size drops as proportionally fewer female skins will be sold.

```{r, echo=FALSE}
qplot(Gen, avg.skin.price.mean, data=summarized) + geom_line(linetype =2) +geom_errorbar(
  aes(
    x = Gen,
    ymin = avg.skin.price.mean - sqrt(avg.skin.price.var),
    ymax = avg.skin.price.mean + sqrt(avg.skin.price.var)
  ),
  width = 0.25,
  data = summarized
)+
  labs(title ="Average skin price", x="Simulation Year", y="Skinprice [DKK]")
```
### Margin per farm pr year

This is calculated as income from skins minus the variable costs+fixed+pelting+feeding
The fixed costs are determined in year 0 by the number of breeding females. Variable costs are fixed pr breeding female and are adjusted within year by the number of breeding females on the farm. Pelting costs are fixed pr pelt and feeding costs are based on the weight of the animals pr farm.


```{r,echo=FALSE}
qplot(Gen, margin.mean, data=summarized) + geom_line(linetype =2) +geom_errorbar(
  aes(
    x = Gen,
    ymin = margin.mean - sqrt(margin.var),
    ymax = margin.mean + sqrt(margin.var)
  ),
  width = 0.25,
  data = summarized
)+
  labs(title ="Pr. farm margin", x="Simulation Year", y="Margin [DKK]")


```

### Costs pr skin

This is calculated as the average sum of all production costs
Variable, fixed, pelting and feeding divided by the number of skins sold within year

```{r,echo=FALSE}
qplot(Gen, costs.pr.sold.skin.mean, data=summarized) + geom_line(linetype =2) +geom_errorbar(
  aes(
    x = Gen,
    ymin = costs.pr.sold.skin.mean - sqrt(costs.pr.sold.skin.var),
    ymax = costs.pr.sold.skin.mean + sqrt(costs.pr.sold.skin.var)
  ),
  width = 0.25,
  data = summarized
)+
  labs(title ="Costs pr skin", x="Simulation Year", y="Costs [DKK]")


```

### Costs pr female

This is calculated as the average sum of all production costs
Variable, fixed, pelting and feeding divided by the number of females at the start of the year

```{r,echo=FALSE}
qplot(Gen, costs.pr.female.mean, data=summarized) + geom_line(linetype =2) +geom_errorbar(
  aes(
    x = Gen,
    ymin = costs.pr.female.mean - sqrt(costs.pr.female.var),
    ymax = costs.pr.female.mean + sqrt(costs.pr.female.var)
  ),
  width = 0.25,
  data = summarized
)+
  labs(title ="Costs pr female", x="Simulation Year", y="Costs [DKK]")


```

### Number of female breeders

The program adjust the number of breeding animals between year to try and optimize cage usage. It uses linear programming to optimize the number subject to the constraint that number of kits should fit into the cages. If there are more kits than it guessed, the farm sells of the extra kits at a fixed prize (80 kr pr kit)

```{r,echo=FALSE}
qplot(Gen, n.females.mean, data=summarized) + geom_line(linetype =2) +geom_errorbar(
  aes(
    x = Gen,
    ymin = n.females.mean - sqrt(n.females.var),
    ymax = n.females.mean + sqrt(n.females.var)
  ),
  width = 0.25,
  data = summarized
)+
  labs(title ="Number of breeding females", x="Simulation Year", y="Costs [DKK]")


```


### Average price of female skins

```{r,echo=FALSE}
  setwd("C:/Users/au384062/Dropbox/Projects/simulation of mink farm/Output/DMU analysis/")

skin.metrics.females <- read.table("skin_metrics_females", header=T, row.names = NULL)
female.skins <- summaryBy(S50/numb.animals + 
                     S40/numb.animals +
                     S30/numb.animals+
                     S00/numb.animals+
                     S0/numb.animals+
                     S1/numb.animals+
                     S2/numb.animals+
                     S3/numb.animals+
                     S4/numb.animals+
                     S5/numb.animals+
                     purple/numb.animals+
                     platinum/numb.animals+
                     burgundy/numb.animals+
                     ivory/numb.animals+
                     vel3/numb.animals+
                     vel2/numb.animals+
                   vel1/numb.animals+
                   kl/numb.animals+
                  long.nap/numb.animals+
                    avg.price.females
                   ~ Gen, data=skin.metrics.females,FUN = c(mean, var))
qplot(Gen, avg.price.females.mean, data=female.skins) + geom_line(linetype =2) +geom_errorbar(
  aes(
    x = Gen,
    ymin = avg.price.females.mean - sqrt(avg.price.females.var),
    ymax = avg.price.females.mean + sqrt(avg.price.females.var)
  ),
  width = 0.25,
  data = female.skins
)+
  labs(title ="Average price of female skins", x="Simulation Year", y="Sales price [DKK]")

```

### Average price of male skins

### Average price of female skins

```{r,echo=FALSE}
  setwd("C:/Users/au384062/Dropbox/Projects/simulation of mink farm/Output/DMU analysis/")

skin.metrics.males <- read.table("skin_metrics_males", header=T, row.names = NULL)

male.skins <- summaryBy(S50/numb.animals + 
                     S40/numb.animals +
                     S30/numb.animals+
                     S00/numb.animals+
                     S0/numb.animals+
                     S1/numb.animals+
                     S2/numb.animals+
                     S3/numb.animals+
                     S4/numb.animals+
                     S5/numb.animals+
                     purple/numb.animals+
                     platinum/numb.animals+
                     burgundy/numb.animals+
                     ivory/numb.animals+
                     vel3/numb.animals+
                     vel2/numb.animals+
                     vel1/numb.animals+
                     kl/numb.animals+
                     long.nap/numb.animals+
                     avg.price.males
                   ~ Gen, data=skin.metrics.males,FUN = c(mean, var))

qplot(Gen, avg.price.males.mean, data=male.skins) + geom_line(linetype =2) +geom_errorbar(
  aes(
    x = Gen,
    ymin = avg.price.males.mean - sqrt(avg.price.males.var),
    ymax = avg.price.males.mean + sqrt(avg.price.males.var)
  ),
  width = 0.25,
  data = male.skins
)+
  labs(title ="Average price of male skins", x="Simulation Year", y="Sales price [DKK]")

```

